Graphical representation example: Alternative interpretations

### 2023-11-23 notebooks/Graphical_representation_alternatives.Rmd
Add control for computing the arc-cosine of the "computational 1" cosine exception

  items                                                                      |>
    tidyr::pivot_longer(!!discrimination, names_to = "par", values_to = "a") |>
    dplyr::group_by(!!item_id)                                               |>
    # This renaming is necessary for accessing the variable in `transmute`:
    dplyr::rename(d = !!intercept)                                           |>
    dplyr::transmute(
      !!item_id,
      ## Compute the multidimensional parameters:
      dim   = par |> stringr::str_extract("\\d+"),
      MDISC = (t(a) %*% cov_matrix %*% a) |> drop() |> sqrt(),
      D     = - d / MDISC,
      cos   = (scale_matrix %*% a / MDISC) |> drop(),
      rad   = acos(cos),
      deg   = rad * RAD_DEG_FACTOR
    )                                                                        |>
    dplyr::ungroup()                                                         |>
    select(!!item_id, dim, MDISC, D, all_of(dir_out))                        |>
    tidyr::pivot_wider(
      names_from  = dim,
      values_from = all_of(dir_out),
      names_glue  = one_dir |> if_else('{.value}_{.name}', '{.name}')
    )
}
```

>>>>

  items                                                                      |>
    tidyr::pivot_longer(!!discrimination, names_to = "par", values_to = "a") |>
    dplyr::group_by(!!item_id)                                               |>
    # This renaming is necessary for accessing the variable in `transmute`:
    dplyr::rename(d = !!intercept)                                           |>
    dplyr::transmute(
      !!item_id,
      ## Compute the multidimensional parameters:
      dim   = par |> stringr::str_extract("\\d+"),
      MDISC = (t(a) %*% cov_matrix %*% a) |> drop() |> sqrt(),
      D     = - d / MDISC,
      cos   = (scale_matrix %*% a / MDISC) |> drop(),
      rad   = dplyr::if_else(
        assertive.numbers::is_equal_to(cos, 1), # If cos is a "computational 1",
        0,                                  # then fill in its arc-cos with a 0;
        suppressWarnings(acos(cos))   # otherwise, compute its arc-cos normally.
      ),
      deg   = rad * RAD_DEG_FACTOR
    )                                                                        |>
    dplyr::ungroup()                                                         |>
    select(!!item_id, dim, MDISC, D, all_of(dir_out))                        |>
    tidyr::pivot_wider(
      names_from  = dim,
      values_from = all_of(dir_out),
      names_glue  = one_dir |> if_else('{.value}_{.name}', '{.name}')
    )
}
```
